\section*{Most Importantly}
\begin{itemize}
\item \textbf{You may not use this compilation for commercial /
  profit-making purposes!}  This is because this compilation uses
  images from the Digitized Sky Surveys, and data from Dr. Wolfgang
  Steinicke's Revised NGC / IC. Please see
  \url{http://gsss.stsci.edu/Acknowledgements/DSSCopyrights.htm} and
  the NGC/IC section of \url{http://www.klima-luft.de/steinicke/} (in
  the German) or \url{http://www.klima-luft.de/steinicke/index_e.htm}
  (in English) for details.
\item \textbf{You may not distribute copies of this compilation
  without the Legal, Acknowledgement and Credits sections}
\item \textbf{No part of the legal, acknowledgement and credits
  sections may be modified or deleted.} The only permissible changes
  are inclusions of your own acknowledgments and copyright statements,
  for both your contributions and acknowledgements for any compatibly
  licensed graphics that you may include.
\item Subject to these terms, \textbf{you are permitted to make
  copies, distribute and modify} this compilation, with the exception
  that the right to modify the DSS or the NGC / IC data is contingent
  on the express permission of the copyright holders of the same.
\end{itemize}

\section{Data Sources and Copyrights}
\begin{itemize}
\item \textbf{Images} from the \emph{Digitized Sky Survey} used in
  this compilation come from the \emph{POSS II} (Northern Hemisphere)
  and \emph{UKSTU} (Southern Hemisphere) surveys. The following
  copyright statement is found on the DSS access portal at the STScI,
  USA
  (\url{http://gsss.stsci.edu/Acknowledgements/DataCopyrights.htm})

  \begin{itemize}
    \item \emph{POSS-II Northern Hemisphere Surveys} -- The compressed
      files of the ``Palomar Observatory - Space Telescope Science
      Institute Digital Sky Survey'' of the northern sky, based on
      scans of the Second Palomar Sky Survey are copyright (c)
      1993-2003 by the California Institute of Technology and are
      distributed herein\footnote{i.e. at the MAST website:
        \url{http://archive.stsci.edu/}} by agreement. All Rights
      Reserved.
    \item \emph{Southern Hemisphere Surveys observed prior to 1993} --
      Southern Hemisphere Surveys were made with the UK Schmidt
      Telescope at the Anglo-Australian Observatory. Plates from these
      surveys have been digitized and compressed by the STScI. The
      digitized images are copyright (c) 1976-1993, jointly by the UK
      SERC/PPARC (formerly Science and Engineering Research
      Council/Particle Physics and Astronomy Research Council, and
      currently the Science and Technology Facilities Council), and
      are distributed herein by agreement. All Rights
      Reserved. Represented by the Wide Field Astronomy Unit at the
      Royal Observatory Edinburgh (ROE).
    \item \emph{Southern Hemisphere Surveys observed since 1993} --
      The ``Second Epoch Survey'' of the southern sky was made by the
      Anglo-Australian Observatory (AAO) with the UK Schmidt
      Telescope. Plates from this survey have been digitized and
      compressed by the STScI. The digitized images are copyright (c)
      1993-2004 by the Anglo-Australian Observatory Board, and are
      distributed herein by agreement. All Rights Reserved.
  \end{itemize}

  \\

  Please note the data use policies of the DSS, available here:
  \url{http://gsss.stsci.edu/Acknowledgements/DSSCopyrights.htm}
  
  In complying with the DSS copyright policy, the creators of this
  compilation intends that this compilation be used only for
  \textbf{non-profit purposes}.

\item \textbf{Star Catalog Data} used in the star charts come from
  three major catalogs: \emph{Hipparcos}, \emph{Tycho 2}, and
  \emph{USNO NOMAD} and rendered using \emph{KStars}.

  \begin{itemize}
    \item \emph{Hipparcos} and \emph{Tycho 2} were obtained from the
      Astronomical Data Center run by the NASA. While the data center
      is now closed, at the time of download, the website said:

      ``All ADC data are public domain unless otherwise stated in the
      ``ReadMe'' file. The data are for scientific use only and have
      no commercial value.''

      As of January 2013, an archive of the old website is still
      accessible here:
      \url{http://web.archive.org/web/20060908091808/http://adc.astro.umd.edu/adc/questions_feedback.html#policies1}

    \item \emph{USNO NOMAD} was obtained from the US Naval Observatory
      (\url{http://www.nofs.navy.mil/nomad/}).

      The ``Privacy and Security Notice'' on USNO's website
      (\url{http://ad.usno.navy.mil/privacy.shtml}) reads:

      ``All information presented on these pages is considered public
      domain and may be distributed or copied unless otherwise
      specified. Use of appropriate byline/photo/image credits is
      requested.''

      No explicit statement is made about the NOMAD catalog in
      particular.
  \end{itemize}

\item \textbf{Deep-Sky Object Data} used in the star charts come from
  the NGC/IC catalog by Wolfgang Steinicke, and that data is Copyright
  (c) 2003 Wolfgang Steinicke
  $\langle$steinicke-zehnle@t-online.de$\rangle$

  The data has been made freely available for \textbf{non-commercial
    use}.

  The Dreyer and SAC descriptions wherever available come from the
  Saguaro Astronomy Club database, and it is freely available for
  non-commercial use.

\item \textbf{Logo of the Bangalore Astronomical Society} is Copyright
  (c) 2007-2013 Harshad R. Joglekar, and is licensed under Creative
  Commons Attribution-NonCommercial-NoDerivs 3.0, with the additional
  condition that the logo be used only to refer to the Bangalore
  Astronomical Society (\url{http://bas.org.in}), which is a
  registered non-profit organization in Bangalore, India. 

  The full text of the license is available here:
  \url{http://creativecommons.org/licenses/by-nc-nd/3.0/}

  Please note the additional condition that the use of the logo in
  reference to anything other than the Bangalore Astronomical Society
  (henceforth referred to as BAS) is prohibited.

  While the logo itself may not be used for commercial purposes, the
  author of the logo makes the exception that collections (as defined
  in section 1b of the license), such as this compilation, containing
  the logo may be used for commercial purposes.

\item \textbf{The icon of KStars} used on the Acknowledgements page is
  part of the Oxygen Project (\url{http://www.oxygen-icons.org/}) of
  KDE. The icon can be copied under the GNU LGPLv3 license, which is
  available here: \url{http://www.gnu.org/copyleft/lesser.html}

  Note the requirements for using this icon in printed material here:
  \url{http://techbase.kde.org/Projects/Oxygen/Licensing#Use_on_Physical_Media}

\item \textbf{The binocular icon} included on some of the pages is in
  the public domain. It was obtained from the website
  \url{http://openclipart.org/}
  
\item \textbf{The city skyline icon} included on some of the pages is
  Copyright (c) by the user soul\_flow on Flickr
  (\url{http://www.flickr.com/photos/soulflow}).

  The original photograph is titled``Bangalore - Modern building'' and
  is available at
  \url{http://www.flickr.com/photos/soulflow/1410390525/} as of this
  writing.

  The photograph is licensed under CreativeCommons 2.0 Attribution
  ShareAlike. The terms of the license may be read at
  \url{http://creativecommons.org/licenses/by-sa/2.0/deed.en}.

  The photograph was posterized and vectorized by Akarsh Simha in
  order to create a vector graphic for use in this compilation.

\end{itemize}

\section{Copyrights of the Compilation}

The production of this compilation in itself is creative work. While
the data content of the compilation does have varying licensing /
copyright policies as detailed above, the compilation itself is
licensed under Creative Commons 3.0 Attribution Share-Alike. The terms
of the license are accessible here:
\url{http://creativecommons.org/licenses/by-nc/3.0/}

Note that the license chosen for the act of compilation itself does
allow for both commercial use and derivative works. In particular,
this likely means that removing the DSS images from all pages, at the
time of this writing, removes necessary restrictions on the commercial
use of this compilation. However, the author is not a lawyer and does
not warrant the accuracy of this claim. Please do your own checks
before trying to use this document for commercial purposes.

The Compilation itself is Copyright (c) 2013 Akarsh Simha.

Akarsh Simha may be reached at $\langle$akarshsimha@gmail.com$\rangle$.

\section{NO WARRANTY}

  BECAUSE THE COMPILATION IS LICENSED FREE OF CHARGE, THERE IS NO
  WARRANTY FOR THE COMPILATION, TO THE EXTENT PERMITTED BY APPLICABLE
  LAW.  EXCEPT WHEN OTHERWISE STATED IN WRITING THE COPYRIGHT HOLDERS
  AND/OR OTHER PARTIES PROVIDE THE DATA AND THE COMPILATION ``AS IS''
  WITHOUT WARRANTY OF ANY KIND, EITHER EXPRESSED OR IMPLIED,
  INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
  MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.  THE ENTIRE
  RISK AS TO THE QUALITY AND ACCURACY OF THE COMPILATION IS WITH YOU.
  SHOULD THE COMPILATION PROVE INACCURATE, YOU ASSUME THE COST OF ALL
  NECESSARY SERVICING, REPAIR OR CORRECTION.

  IN NO EVENT UNLESS REQUIRED BY APPLICABLE LAW OR AGREED TO IN
  WRITING WILL ANY COPYRIGHT HOLDER, OR ANY OTHER PARTY WHO MAY MODIFY
  AND/OR REDISTRIBUTE THE COMPILATION AS PERMITTED ABOVE, BE LIABLE TO
  YOU FOR DAMAGES, INCLUDING ANY GENERAL, SPECIAL, INCIDENTAL OR
  CONSEQUENTIAL DAMAGES ARISING OUT OF THE USE, OR INABILITY TO USE,
  OR THE INACCURACY OF THE COMPILATION (INCLUDING BUT NOT LIMITED TO
  INACCURACIES OF SUBSEQUENTLY COMPUTED DATA AND LOSSES SUSTAINED BY
  YOU OR THIRD PARTIES), EVEN IF SUCH HOLDER OR OTHER PARTY HAS BEEN
  ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.

