This is a log book for observers wanting to see more bright galaxies
in the sky, but have already finished the Bright Galaxies logbook, or
have more aperture power, or want to try something more adventurous.

This is a compilation of observation log forms for each of the objects
accompanied by useful information about the object, 3 star charts, and
an image from the Digitized Sky Surveys. It may gain more features as
time progresses.

The book contains 64 objects to add to the 180 objects from the
``Bright Galaxies Logbook''. All of the galaxies listed in this
logbook are expected to be visually observable with an 8-inch (200mm)
telescope, from reasonably dark (Bortle 4) skies. Of course, many of
them are visible in smaller aperture too, so you can still use this
logbook if you run out of objects.

Galaxies were programmatically chosen from the SAC database
(\url{http://www.saguaroastro.org/content/downloads.htm}) by applying
the following filters:
\begin{itemize}
\item Galaxy not a Messier object
\item Galaxy is marked pB in Dreyer's descriptions
\item Galaxy is brighter than 11.0 mag (to avoid tiny, high-surface
  brightness galaxies)
\end{itemize}
Since there was no human intervention involved, there could be
errors. However, I checked that most of the galaxies I considered
significant, that were not present in the ``Bright Galaxies Logbook''
are present in this extension.

Many of these galaxies may not be visible at your latitude. The book
is hemisphere-neutral, and just lists objects irrespective of southern
/ northern declination. It is important to note that objects low in
the horizon are made substantially more difficult by airmass.

The book's content and structure is inspired by the Bangalore
Astronomical Society's (\url{http://bas.org.in}) observer
certification programs. The idea for this particular logbook came from
Mr. Naveen Nanjundappa.

Hope you will enjoy observing these galaxies!

\\

\hfill --Akarsh Simha
